Enhancing Underwater Imagery using Generative Adversarial Networks

### 2017-09-28 files/paper/PlainPaper.tex
update

\title{Enhancing Underwater Imagery using Generative Adversarial Networks}
\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
\thanks{				
  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA,
  and the $^{1}$Air Force Research Laboratory, Rome, NY \newline
 {\tt\small\{$^{1}$fabbr013, $^{2}$islam034, $^{3}$junaed\}@umn.edu}
 {\tt\small$^{1}$cameron.fabbri@us.af.mil}
}
}

\begin{document}
\maketitle

>>>>

\title{Enhancing Underwater Imagery using Generative Adversarial Networks}
\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
\thanks{				
  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA,
  and the $^{1}$Air Force Research Laboratory, Rome, NY \newline
 {\tt\small\{$^{1}$cameron.fabbri@us.af.mil\}} \newline
 %, fabbr013@umn.edu\}} \newline
 {\tt\small\{$^{1}$fabbr013,$^{2}$islam034, $^{3}$junaed\}@umn.edu}
}
}

\begin{document}
%\twocolumn[{%
%\renewcommand\twocolumn[1][]{#1}%
%\maketitle
%\begin{center}
%    \centering
%    \includegraphics[width=5in]{V8PYG3g}
%\end{center}%
%}]

\maketitle
